Realizing Temporal Graphs

### 2023-02-01 Older Versions/OLD-OLD-RealizingTemporalGraphs.tex
Changes 31st Jan

\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate,anonymous]{lipics-v2021}
%This is a template for producing LIPIcs articles. 
%See lipics-v2021-authors-guidelines.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling autoref support, use "autoref"
%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
%for enabling thm-restate support, use "thm-restate"
%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
%for producing a PDF according the PDF/A standard, add "pdfa"

%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\usepackage{amsmath}
%\let\proof\relax
%\let\endproof\relax

@@

\usepackage{comment}

@@

\crefname{claim}{Claim}{Claims}

@@

\newcommand{\ie}{i.\,e.,\ }
\renewcommand{\st}{s.\,t.,\ }
\newcommand{\NP}{\textrm{NP}}
\newcommand{\APX}{\textrm{APX}}
\newcommand{\FPT}{\textrm{FPT}}
\newcommand{\XP}{\textrm{XP}}

@@

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{Realizing temporal graphs from fastest travel times} %TODO Please add

%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line

%\author{Nina Klobas}{Department of Computer Science, Durham University, UK}{nina.klobas@durham.ac.uk}{ https://orcid.org/0000-0002-8024-5782}{}

%\author{George B. Mertzios}{Department of Computer Science, Durham University, UK}{george.mertzios@durham.ac.uk}{https://orcid.org/0000-0001-7182-585X}{Supported by the EPSRC grant EP/P020372/1.}

%\author{Hendrik Molter}{Department of Industrial Engineering and Management, Ben-Gurion~University~of~the~Negev, Israel}{molterh@post.bgu.ac.il}{https://orcid.org/0000-0002-4590-798X}{Supported by the ISF, grant No.~1070/20.}

%\author{Paul G. Spirakis}{Department of Computer Science, University of Liverpool, UK}{p.spirakis@liverpool.ac.uk}{https://orcid.org/0000-0001-5396-3749}{Supported by the EPSRC grant EP/P02002X/1.}

%\authorrunning{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

%\Copyright{Nina Klobas, George B. Mertzios, Hendrik Molter, and Paul G. Spirakis} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[500]{Theory of computation~Graph algorithms analysis}
\ccsdesc[500]{Mathematics of computing~Discrete mathematics}
%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{Temporal graph, periodic temporal labeling, fastest temporal path, graph realization, temporal connectivity.} %TODO mandatory; please add comma-separated list of keywords

\category{} %optional, e.g. invited paper

\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversiondetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93]{Classification (e.g. Full Version, Extended Version, Previous Version}{URL to related version} %linktext and cite are optional

%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
%\supplementdetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g. Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

%\acknowledgements{I want to thank \dots}%optional

%\nolinenumbers %uncomment to disable line numbering

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle

\begin{abstract}
In this paper we study \emph{temporal design} problems of undirected temporally connected graphs. 
The basic setting of these optimization problems is as follows: given an undirected graph~$G$, 
what is the smallest number $|\lambda|$ of time-labels that we need to add to the edges of $G$ such that the resulting temporal graph $(G,\lambda)$ is temporally connected?

\vspace{0,2cm}
\noindent \textbf{Due to lack of space, the full paper with all proofs is attached in a 
	clearly marked Appendix to be read at the discretion of the Program Committee.}
\end{abstract}

\section{Introduction}\label{intro-sec}

Graph realization problems are fundamental graph-algorithmic questions where the objective is to (re)construct a graph, 
given some constraints on some of its graph attributes. Among the most well studied such parameters for graph reconstruction 
are the vertex degrees~\cite{}, distances~\cite{}, eccentricities~\cite{}, connectivity~\cite{}, etc. 
The motivation for network realization problems stems from both ``verification'' applications where we attempt to reconstruct an existing network of unknown structure based on the outcomes of experimental measurements, and engineering applications related to network design~\cite{.....}.

@@

Next, consider the validation gadget for color $i$. 
%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
%\begin{itemize}
    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
%\end{itemize}
%
For all $0\le j<j'<i$ and all $i<j<j'\le k$ we set the following.
\begin{itemize}
    \item We set $d(v^i_j,v^i_{j'})=6(j'-j)-1$.
\end{itemize}
The next cases are only relevant if $1\neq i \neq k$. 
For all $0\le j<i$ and $\ell\in[n+3]$ we set the following.
\begin{itemize}
    \item We set $d(v^i_j,\hat{u}^i_{\ell})=6(i-j-1)+2\ell-1$.
\end{itemize}
For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
\begin{itemize}
    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
\end{itemize}
For all $0\le j<i$ and all $i<j'\le k$ we set the following.
\begin{itemize}
    \item We set $d(v^i_j,v^i_{j'})=6(j'-j)+2n-1$.
\end{itemize}
For all $\ell\in[n+3]$ and $i<j\le k$ we set the following.
\begin{itemize}
    \item We set $d(\hat{u}^i_{\ell},v^i_j)=6(j-i)+2(n-\ell)+5$.
\end{itemize}

@@

\begin{figure}%[t]
\noindent\makebox[\textwidth]{
\centering
%\begin{center}
\begin{tikzpicture}[line width=1pt, scale=.65]
\scriptsize
\node (A) at (12,0) {};

\draw[rounded corners, dashed, gray] (-13, 5) rectangle (8, 1.5) {};
\node (A) at (-10.5,4.5) {alignment gadget};

@@

Let us denote with $Z$ the set of vertices removed from $G$ at the beginning of the algorithm, \ie $Z = V(G) \setminus V(G')$.
By the construction it follows that $Z$ consists of disjoint trees. 
Note that the fastest temporal paths among vertices of $G'$ are independent of vertices in $Z$.
Let us remember the following basic property of the problem \deltaExact.
A labeling $\lambda$ of $G$ satisfies $D$ if every fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$,
and none other temporal path from $v_i$ to $v_j$ is faster.
In order to find a labeling that satisfies this property we split our analysis in nine cases,
where the first vertex is in one of the sets $U,V(G') \setminus U, Z$,
and similarly the last vertex is in one of the sets $U,V(G') \setminus U, Z$.
In each of these cases we guess the underlying path $P$ of the fastest temporal path from the vertex $v_i$ to $v_j$, 
which results in one equality constraint for the labels on the path $P$. 
For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
This results in producing $poly(n,m)$ constraints. We have to guarantee only, that the number of guesses, of faster temporal paths, is exponential in $k$ and not in $n$.

>>>>

\documentclass[11pt,a4paper]{article}

\usepackage[english]{babel}

\usepackage{fullpage}

\usepackage{amsmath}
\let\proof\relax
\let\endproof\relax

@@

\newtheorem{theorem}{Theorem}
\newtheorem{observation}{Observation}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conjecture}[theorem]{Conjecture}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[definition]{Example}
\usepackage{comment}

@@

\usepackage[capitalise,nameinlink, noabbrev]{cleveref}
\crefname{claim}{Claim}{Claims}
\crefname{observation}{Observation}{Observations}

\usepackage{authblk}

@@

\newcommand{\ie}{i.\,e.,\ }
\newcommand{\st}{s.\,t.,\ }
\newcommand{\NP}{\textrm{NP}}
\newcommand{\APX}{\textrm{APX}}
\newcommand{\FPT}{\textrm{FPT}}
\newcommand{\XP}{\textrm{XP}}

@@

\title{Realizing Temporal Graphs}
\author{Nina Klobas, George B. Mertzios, Hendrik Molter, Paul G. Spirakis}

\bibliographystyle{abbrv}
\begin{document}
	\maketitle

@@

Next, consider the validation gadget for color $i$. 
%Let $1\le j<i$, let $e_\ell\in F_{j,i}$, and let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. We set the following.
%\begin{itemize}
    %\item We set $d(v^i_{j-1},w^i_{\ell'+1})=3$.
    %\item We set $d(w^i_{\ell'},v^i_{j})=3$.
%\end{itemize}
%
For all $0\le j<j'<i$ and all $i<j<j'\le k$ we set the following.
\begin{itemize}
    \item We set $d(v^i_j,v^i_{j'})=6(j'-j)-1$.
\end{itemize}

The following cases are only relevant if $1\neq i \neq k$. 
For all $0\le j<i$ and $\ell\in[n+3]$ we set the following.
\begin{itemize}
    \item We set $d(v^i_j,\hat{u}^i_{\ell})=6(i-j-1)+2\ell-1$.
\end{itemize}
For all $\ell,\ell'\in[n+3]$ with $\ell<\ell'$ we set the following.
\begin{itemize}
    \item We set $d(\hat{u}^i_{\ell},\hat{u}^i_{\ell'})=2(\ell'-\ell)-1$.
\end{itemize}
For all $0\le j<i$ and all $i<j'\le k$ we set the following.
\begin{itemize}
    \item We set $d(v^i_j,v^i_{j'})=6(j'-j)+2n-1$.
\end{itemize}
For all $\ell\in[n+3]$ and $i<j\le k$ we set the following.
\begin{itemize}
    \item We set $d(\hat{u}^i_{\ell},v^i_j)=6(j-i)+2(n-\ell)+5$.
\end{itemize}

@@

\begin{figure}%[t]
\noindent
\makebox[\textwidth]{
\centering
%\begin{center}
\begin{tikzpicture}[line width=1pt, scale=.65]
\scriptsize
\draw[rounded corners, dashed, gray] (-13, 5) rectangle (8, 1.5) {};
\node (A) at (-10.5,4.5) {alignment gadget};

@@

Let us denote with $Z$ the set of vertices removed from $G$ at the beginning of the algorithm, \ie $Z = V(G) \setminus V(G')$.
By the construction it follows that $Z$ consists of disjoint trees. %%TBDNKL
Note that the fastest temporal paths among vertices of $G'$ are independent of vertices in $Z$.
Let us remember the following basic property of the problem \deltaExact.
A labeling $\lambda$ of $G$ satisfies $D$ if every fastest temporal path from vertex $v_i$ to $v_j$ equals $D_{v_i, v_j}$,
and none other temporal path from $v_i$ to $v_j$ is faster.
In order to find a labeling that satisfies this property we split our analysis in nine cases,
where the first vertex is in one of the sets $U,V(G') \setminus U, Z$,
and similarly the last vertex is in one of the sets $U,V(G') \setminus U, Z$.
In each of these cases we guess the underlying path $P$ of the fastest temporal path from the vertex $v_i$ to $v_j$, 
which results in one equality constraint for the labels on the path $P$. 
For all other temporal paths from $v_i$ to $v_j$ we know that they cannot be faster, so we introduce inequality constraints for them.
This results in producing $poly(n,m)$ constraints. We have to guarantee only, that the number of guesses, of faster temporal paths, is exponential in $k$ and not in $n$.
